---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```
e-Stat API for R
==========================
[![Travis-CI Build Status](https://travis-ci.org/yutannihilation/estatapi.svg?branch=master)](https://travis-ci.org/yutannihilation/estatapi)
[![AppVeyor Build Status](https://ci.appveyor.com/api/projects/status/github/yutannihilation/estatapi?branch=master&svg=true)](https://ci.appveyor.com/project/yutannihilation/estatapi)
[![CRAN_Status_Badge](http://www.r-pkg.org/badges/version/estatapi)](http://cran.r-project.org/package=estatapi)

## e-Stat API

e-Stat is a service to get Statistics of Japan, which is provided by Japanese Government. See http://www.e-stat.go.jp/api/.

**The contents of e-Stat is not garanteed by Japanese Government**

## Requirement

First, You need to register at e-Stat website to obtain `appId`.

## Installation

```{r, eval=FALSE}
# Stable version
install.packages("estatapi")

# Development version
devtools::install_github("yutannihilation/estatapi")
```

## Usage

Currently, this package supports four methods of API v2. For the details about the query params, please read the official documentation at http://www.e-stat.go.jp/api/e-stat-manual/

### estat_getStatsList

Get list of statistics matched with the provided query.

This function returns result as a `tbl_df`.

```{r, eval=FALSE}
appId <- "XXXXXXXXX"
```

```{r, echo=FALSE,message=FALSE}
library(dplyr)

appId <- readr::read_lines(".appId")
```

By default, the language of the datasets is Japanese.

```{r}
library(estatapi)

estat_getStatsList(appId = appId, searchWord = "chocolate")
```

You can add `lang = "E"` to search for English datasets. But be careful, not all datasets are translated into English and the translation may be wrong sometimes...

```{r}
estat_getStatsList(appId = appId, lang = "E", searchWord = "chocolate")
```

### estat_getMetaInfo

Get meta-information about the data.

This function returns a list of `tbl_df`. Each `tbl_df` contains the meta-info for the correspondent column.

```{r}
meta_info <- estat_getMetaInfo(appId = appId, lang = "E", statsDataId = "0003036792")

names(meta_info)

meta_info$cat01
```


### estat_getStatsData

Get statistics.

Though only `appId` and `statsDataId` are required, I recommend you to use additional condition to save time.

```{r}
estat_getStatsData(
  appId = appId,
  lang = "E",
  statsDataId = "0003036792",
  cdCat01 = c("0005","1021")
)
```

You may feel convenient with `limit` and `startPosition` to get data partially.

```{r}
d1 <- estat_getStatsData(
        appId = appId, lang = "E", statsDataId = "0003036792", cdCat01 = c("0005","1021"),
        limit = 
      )

d2 <- estat_getStatsData(
        appId = appId, lang = "E", statsDataId = "0003036792", cdCat01 = c("0005","1021"),
        startPosition=101,
        limit = 3
      )
#> There are more records; please rerun with startPosition=201

d <- bind_rows(d1, d2)
```

### getDataCatalog

Find statistical dataset files (Excel, CSV and PDF) and databases.

Note that this API returns only URL of the file or database and the data itself is not accessible via e-Stat API.
You can download the file from the given URL, but it may be difficult to process the data by R.

```{r}
catalog1 <- estat_getDataCatalog(appId = appId, lang = "E", searchWord = "population", dataType = c("PDF", "XLS"))

catalog1[1, c("@id", "STAT_NAME", "TABLE_NAME", "SURVEY_DATE", "TABLE_SUB_CATEGORY1", "DATASET_NAME", "NAME", "LANDING_PAGE", "URL", "FORMAT")] %>%
  glimpse
```
